
%====================
% Teaching Assistant
%====================
\subsection{{iOS Teaching Assistant \hfill Sep 2022 --- Nov 2022}}
\subtext{Codepath \hfill Remote, U.S.}
\begin{zitemize}
\item Lead breakout room sessions with students to assist with student projects.
\item Communicated with students after class to assist in debugging or general questions.

\end{zitemize}


%====================
% EXPERIENCE A
%====================
\subsection{{Software Engineering Intern \hfill Jun 2022 --- Aug 2022}}
\subtext{Meta \hfill Menlo Park, California}
\begin{zitemize}
\item Collaborated with cross-functional teams to implement a feature that reduced negative messaging interactions on the Instagram iOS app by 14\%.
\item Responsible for scoping and executing the early stages of a new project, collaborating closely with server engineers and Android engineers to ensure uniform implementation across platforms.
\item Prepared and presented design doocuments to members of th team.
\item Wrote unit tests using Jest and XCTest.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Facebook University Intern \hfill Jun 2021 --- Aug 2021}}
\subtext{Meta \hfill Remote, U.S.}
\begin{zitemize}
\item Developed an iOS Application using the MVC pattern from start to finish including interface design and implementation.
\item Utilized the iOS Google Maps SDK to display user paths.
\item Implemented a custom algorithm to optimize user path storage and performance, resulting in a reduction of \href{https://docs.google.com/document/d/1MRAG9OrrXqONw2qEdH7BeSrUC1HFEtD6CoXgO1jC910/edit?usp=sharing}{\bf up to 60\%} in the number of points stored.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{iOS Instructor \hfill Jan 2021 --- May 2021}}
\subtext{Codepath \hfill Remote, U.S.}
\begin{zitemize}
\item Taught a class of 20+ students, alongside 4 other students, on how to use XCode to create their own iOS Apps.
\item Followed the \href{https://www.codepath.org/courses/ios-mobile-development}{Codepath iOS Mobile Development Curriculum}.
\item Explained concepts to students such as delegate patterns and using autolayout with swift.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
