\subsection{{CampusBuddy | \href{https://github.com/pegliang/CampusBuddy}{Github} \hfill February 2023 --- Present}}
\begin{zitemize}
\item Collaborated with a team of six to develop CampusBuddy, a cross-platform app designed to connect students for study groups and networking purposes.
\item Implemented a real-time messaging service, using Socket.io for the live user connections, MongoDB to persist user messages, and Flutter to build the frontend.
\item Created API endpoints for user matching using Pandas for recommendations, Flask for serving endpoints, and MongoDB for storing user interactions, resulting in personalized suggestions for users.
\end{zitemize}

\subsection{{Live Video Translator Extension | \href{https://github.com/jerikjakobsen/Translator-Extension}{Github} \hfill March 2023 --- Present}}
\begin{zitemize}
\item Developed a Chrome extension that lets users access live video translations in languages supported by Microsoft Azure Speech Service, improving user experience.
\item Utilized JavaScript for extension development and employed Node.js and Socket.io to build a responsive backend server.
\end{zitemize}

\subsection{{CyberSafe | \href{https://github.com/jerikjakobsen/CyberSafe}{Github} \hfill Jul 2022 --- Present}}
\begin{zitemize}
\item Developed a full-stack iOS application enabling users to securely store and access their passwords.
\item Built a RESTful API using Node.js and Express, and integrated it with an Amazon Web Services (AWS) S3 Bucket for data storage and retrieval.
\item Adhered to the Keepass KDBX file format, ensuring security by implementing AES encryption and decryption for user data protection and confidentiality.
\end{zitemize}